|

### 2024-08-20 reproducibility/manuscript/manuscript.qmd
chore(manuscript): add cytotrace methods
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

## Model formulation {#sec-model}

@@

## Model evaluation and selection {#sec-model-selection}

>>>>

## Model formulation {#sec-methods-model}

@@

## Cytotrace model {#sec-methods-cytotrace}

We implemented Cytotrace in Python based on the R version [@Gulati2020-xq] for
benchmarking Pyro&thinsp;-Velocity and scVelo’s shared (latent) time prediction in the
Python environment. This implementation is available in the 
[Pyro&thinsp;-Velocity GitHub repository](https://github.com/pinellolab/pyrovelocity/blob/main/src/pyrovelocity/analysis/cytotrace.py).

## Model evaluation and selection {#sec-methods-model-selection}
